### 2013-07-05 tests_Kinematics.Rmd
some bugs removed

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=300)

@@

save(report, file="Kinematics300.Rda") # recover with load("Kinematics.Rda")

df <- data.frame(ga.poly = report$ga.error,
                 lin.reg = report$lm.error,
                 svm = report$svm.error,
                 rpart = report$rpart.error,
                 rf = report$rf.error,
                 ci.tree = report$citree.error)

@@

write.table(df, "lambda.errors.kinematics.txt")

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Kinematics dataset")

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=200, iterations=100)

@@

save(report, file="Kinematics200.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "lambda.errors.kinematics2.txt")

df <- read.table("lambda.errors.kinematics2.txt", header=TRUE)

df$lambda <- as.factor(df$lambda)

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Kinematics dataset")
##############################################
# Check fitness progress

source("gapolyfuncs.R")
follow.fitness(my.data,population=300,iterations=50,mutation.rate=0.15,lambda=0.95)
